Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-16 trunk/constantRate/ConstCompFuzzExt-reorg.tex
minor updates and bib cleanup

\begin{table}
\begin{tabular}{l | l | l | l }
Construction & Security & Features & Limitations \\
\hline
\consref{cons:info theoretic} & Info-theoretic & Exploits distribution & Most symbols must \\
&&structure & contribute fresh entropy \\\hline
\consref{cons:sampling} & Computational  & Reusable with arbitrary & Error tolerance is\\
&&correlation & sub-constant fraction\\\hline
\consref{cons:first construction} & Computational & Supports distributions  & Super-polynomial \\
& &  with dependent symbols & size symbols
\end{tabular}
\caption{Summary of new constructions.  All constructions support families of distributions with $\Huse \le 0$.}
\label{tab:upper bounds}
\end{table}

@@

\paragraph{Connection to General Obfuscation}
\bnote{needs to be rewritten}
We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions. Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs. However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model. The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero. However, we do not know if these functions include proximity point programs.

@@

Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.  That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.  This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.  There are two basic versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security), and second where the adversary also sees some subset of the derived keys as well~(insider security).  Ideally, we want $w_1,..., w_q$ and the unseen keys to be ``as good'' as in the single use case.  Boyen constructs a reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes.  For simplicity here, we define the insider security and note any scheme that achieves insider security also achieves outsider security.

\paragraph{Previous Results}

There are two primary questions about the reusability of a fuzzy extractor.  The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.  Boyen~\cite{Boyen2004} considers fuzzy extractors that are reusable an unbounded number of times.  Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.  They show in the setting of unbounded reuse such a strong restriction on correlation is necessary~\cite[Theorem 11]{Boyen2004}.  In particular, they show how any information-theoretic fuzzy extractor secure with unbounded reuse can be transformed into their construction.  However, there is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.

However, their negative result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.  There are two natural restrictions to the definition of reusability: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.  The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.

We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
%We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
%\begin{definition}[Insider Reusable Fuzzy Extractors]
%\label{def:reusable fuzz}
%Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.  Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.  We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
%\begin{align*}
%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
%\end{align*}
%\end{definition}
Our definition is a modified form of the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We first present the modified definition and then discuss the differences between our definition and that of Boyen.
\begin{definition}[Outsider Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game~(for each $W_1\in \mathcal{W}$ and for all $i=1,..., q$):
\begin{itemize}
\item[Sampling] The challenger samples $w_1\leftarrow W_1$.
\item[Perturbation] For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.  The challenger sets $w_{i+1} = \delta_i(w_1)$.
\item[Distinguishing] The advantage of $D$ is
\[
\epsilon_{sec}\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1] - \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\]
where $u$ is a uniformly random string.
\end{itemize}
Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  We say that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D$ of size at most $s_{sec}$ they win the game with advantage at most $\epsilon_{sec}$.
\end{definition}

\paragraph{Adapting the definition of Boyen to the computational setting:} 
The definition of Boyen considers a single adversary.  We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.  The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.  However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to require the entire adversary to be computationally bounded.  Our construction satisfies this alternative adaption as well.}

@@

\subsection{Obfuscation}
Our constructions will use obfuscation for two types of circuits: point functions and digital lockers. The family of point functions $\mathtt{I}_n = \{I_w\}_{w \in \zo^n}$ defined as follows:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
and the class of digital lockers is $\mathtt{I}_n = \{I_{w, r}\}_{w \in \zo^n, r\in\zo^\kappa}$ defined as follows:
\[
I_{w, r}(x):\begin{cases} r & x=w\\\perp & \text{otherwise}\end{cases}.
\]
The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}. This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}), as it allows the simulator to run in unbounded time while making at most a polynomial number of oracle queries to the function. In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input. Composable auxiliary-input VGB obfuscators for point functions and digital lockers are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points. They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.

%\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.  %Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.  Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.  Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.  In order to provide any meaningful security guarantee, the source distribution must be restricted.  See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:

\section{Supporting more errors than entropy}
\label{sec:info theory cons}
In this section we show an information-theoretic fuzzy conductor that supports more errors than entropy.
Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
The main idea of this construction is to condense entropy from each block of the source and then apply a secure sketch to the condensed blocks.  The main idea is to correct errors on a large alphabet~(before condensing) while paying for the error correction on a smaller alphabet~(after condensing).%Alternatively, this construction can simply be seen as replacing the computational point function obfuscation with an information-theoretic point-function obfuscation~(this is only possible for high enough entropy levels).

\begin{construction}
\label{cons:info theoretic}
Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  We describe $\gen, \rep$ as follows:
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item Sample $seed_i\leftarrow \zo^d$.
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Set $ss \leftarrow \sketch(v_1,..., v_\gamma)$.
\item Set $p = (ss, seed_1,..., seed_\gamma)$.
\item Output $(v, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p = (ss, seed_1,..., seed_\gamma))$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Output $v = \rec(v', ss)$.
\end{enumerate}
\vspace{0.7in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\begin{lemma}
\label{lem:info theory sec}
Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ wand let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon)$-average case randomness conductor.  Let $(\sketch, \rec)$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \tilde{m}, t)$-secure sketch with error $\delta$.~(Convertible to a fuzzy extractor using~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}).

@@

\subsection{When is $\Huse\le 0$?}

\consref{cons:info theoretic} supports partial block sources with $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$.  This means that the input entropy to the secure sketch is $\Theta(\gamma)$.  Standard secure sketches correct a constant fraction of errors at a entropy loss, yielding $\tilde{m} = \Theta(\gamma)$.  Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
More formally:
\[
\Huse(W) = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - \Theta(\gamma) \log |\mathcal{Z}| <0
\]
That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with $\Huse\le 0$.  Furthermore, the construction has super-logarithmic output entropy since $\tilde{m} = \Theta(\gamma) = \omega(\log n)$.

\section{Achieving Reusability \& $\Huse\le 0$}
\label{sec:sampling}
In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with $\Huse \le 0$.  In this section we show that computational techniques allow for additional desirable properties.  Using computational techniques we are able to retain many of the advantages of \consref{cons:info theoretic} and achieve a reusable fuzzy extractor.  This is known to be impossible in the information-theoretic setting.  
%\consref{cons:first construction} is a computational fuzzy conductor with $\Huse\le 0$.  Unfortunately, it requires many blocks of $W$ to have super-logarithmic min-entropy.  In this section, we reduce the required entropy of blocks by obfuscating several blocks simultaneously, at the price of  decreasing the effective error tolerance.
%In this section, we present a generalization where blocks are not individually obfuscated, instead several blocks are obfuscated together~(these blocks are selected using an oblivious sampler).

The main idea is to sample a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscate the concatenation of these blocks.  Denote this concatenated value by $V_1$.  This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct to ``unlock'' the correct key.  
Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.

@@

\noindent
%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
%\begin{itemize}
%\item Multiple blocks are concatenated together.  This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.  
%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.  This requires the use of digital lockers in place of point obfuscations.  Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.  \consref{cons:first construction} only hid part of the key in each obfuscation.  This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.  This construction works for an arbitrary size alphabet.  We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
%\end{itemize}
The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.  Indeed, this is the property that allows this fuzzy extractor to be reusable~(we define reusability in \defref{def:reusable fuzz}).

@@

\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
%We now return to showing \thref{thm:sampling}.  
In this section we briefly describe why \consref{cons:sampling} is secure.  A proof of security appears \apref{sec:analysis sampling}.  
In order to show security \consref{cons:sampling}, we
show that with overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
% forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).  
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.  
We begin by showing that each $V_i$ is statistically close to a high entropy distribution.   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

Once all $V_i$ all simultaneously have good entropy, the adversary will never see anything but $\perp$ as an output from the obfuscations~(with overwhelming probability).  If the adversary only sees $\perp$ from the obfuscations, they have no information about the key.

@@

\subsection{Correctness of \consref{cons:sampling}}
\label{sec:correct sampling}
We are encoding the entire key in each obfuscation.  For correctness, at least one of the repeated readings must be correct with overwhelming probability.  Let $V_i$ represent one of the initial readings and $V_i'$ represent a repeated reading.  For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$.

\begin{lemma}[Proof in \apref{sec:analysis sampling}]
\label{lem:sampling errors}
Let all the variables be as in \thref{thm:sampling}.
 Then $\Pr[\forall i, v_i\neq v_i'] <1 - \ngl(n)$, where the probability is over the coins of $\gen$.  
\end{lemma}

>>>>

\begin{table}
\begin{tabular}{l | l | l | l }
Construction & Security & Features & Limitations \\
\hline
\consref{cons:info theoretic} & Info-theoretic & Exploits distribution & Most symbols must \\
&&structure & contribute fresh entropy \\\hline
\consref{cons:sampling} & Computational  & Reusable with arbitrary & Error tolerance is\\
&&correlation & sub-constant fraction\\\hline
\consref{cons:first construction} & Computational & Supports distributions  & Super-polynomial \\
& &  with dependent symbols & size symbols
\end{tabular}
\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
\label{tab:upper bounds}
\end{table}

@@

\paragraph{Connection to General Obfuscation}
\bnote{needs to be rewritten}
We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions. Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{brakerski2014virtual,barak2014protecting} for all programs. However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model. The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero. However, we do not know if these functions include proximity point programs.

@@

Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.  That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.  This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.  Boyen considers two versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security).  Second where the adversary controls some subset of the servers and sees key generation on arbitrary $p$~(insider security).  
Boyen constructs a outsider reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes. Boyen also transforms this construction in an insider secure construction using random oracles. 
\paragraph{Previous Negative Results}

There are two primary questions about the reusability of a fuzzy extractor.  The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.  Boyen~\cite{Boyen2004} considers fuzzy extractors that are reusable an unbounded number of times.  Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.  They then show information-theoretic fuzzy extractors secure with unbounded reuse can be transformed into their construction~\cite[Theorem 11]{Boyen2004}.  This shows that correlation between $w_1,..., w_q$ must be restricted to this limited class.  There is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.  Their result can be interpreted as saying that reusability is impractical.

However, this result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.  There are two  restrictions to avoid this result: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.  The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.

We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
%We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
%\begin{definition}[Insider Reusable Fuzzy Extractors]
%\label{def:reusable fuzz}
%Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.  Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.  We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
%\begin{align*}
%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
%\end{align*}
%\end{definition}
Our definition is a modified form of the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We discuss definitional differences in \apref{sec:comparing reusability}.

\begin{definition}[Outsider Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$ and fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
\begin{enumerate}%[leftmargin=-.6in]
\item[Sampling] The challenger samples $w_1\leftarrow W_1$.
\item[Perturbation] For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.  The challenger sets $w_{i+1} = \delta_i(w_1)$.
\item[Distinguishing] The advantage of $D$ is
\[
\epsilon_{sec}\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1] - \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\]
where $u$ is a uniformly random string.
\end{enumerate}
Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  We say that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D$ of size at most $s_{sec}$ they win the game with advantage at most $\epsilon_{sec}$.
\end{definition}

@@

\subsection{Obfuscation}
Our constructions will use obfuscation for two types of circuits: point functions and digital lockers. The family of point functions $\mathtt{I}_n = \{I_w\}_{w \in \zo^n}$ defined as follows:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
and the class of digital lockers is $\mathtt{I}_n = \{I_{w, r}\}_{w \in \zo^n, r\in\zo^\kappa}$ defined as follows:
\[
I_{w, r}(x):\begin{cases} r & x=w\\\perp & \text{otherwise}\end{cases}.
\]
The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}. This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}), as it allows the simulator to run in unbounded time while making at a polynomial number of oracle queries to the function. VGB obfuscators for point functions and digital lockers are constructible from specific number-theoretic assumptions or by strong assumptions on hash functions.  We provide more details and a formal definition in \apref{sec:obfuscation def}.

\section{Supporting more errors than entropy}
\label{sec:info theory cons}
In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy.
%Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
The construction first condenses entropy from each block of the source and then applies a different fuzzy extractor to the condensed blocks. We'll denote the fuzzy extractor on the smaller alphabet as $(\gen', \rep')$.  A condenser is like a randomness extractor but the output is allowed to be slightly entropy deficient.  Condensers are known with smaller entropy loss than possible for randomness extractors~(e.g.~\cite{dodis2014key}).  
\begin{definition}
\label{def:conductor}
A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
\end{definition}

The main idea of the construction is that errors are ``corrected'' on the large alphabet~(before condensing) while the entropy loss for the error correction is incurred on a smaller alphabet~(after condensing).

\begin{construction}
\label{cons:info theoretic}
Let $\mathcal{Z}$ be an alphabet and let $W=W_1,..., W_\gamma$ be a distribution over $\mathcal{Z}^\gamma$.  We describe $\gen, \rep$ as follows:
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item Sample $seed_i\leftarrow \zo^d$.
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Set $(r, p') \leftarrow \gen(v_1,..., v_\gamma)$.
\item Set $p = (p', seed_1,..., seed_\gamma)$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p = (p', seed_1,..., seed_\gamma))$
\item For $j=1,..., \gamma$:
\begin{enumerate}[(i)]
\item Set $v_i = \cond(w_i, seed_i)$.
\end{enumerate}
\item Output $r = \rep'(v', ss)$.
\end{enumerate}
\vspace{0.7in}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\begin{lemma}
\label{lem:info theory sec}
%Let $n$ be a security parameter and let $\gamma = \omega(\log n)$.
Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ and let $\cond: \mathcal{Z} \times \zo^d\rightarrow \mathcal{Y}$ be a $(\alpha, \tilde{\alpha}, \epsilon_{cond})$-randomness conductor.  Let $(\gen', \rep')$ be $(\mathcal{Y}^\gamma, \tilde{\alpha}(\gamma - \beta), \kappa, t, \epsilon_{fext})$-fuzzy extractor with error $\delta$.\footnote{We actually need $(\gen', \rep')$ to be an average case fuzzy extractor~(see \cite[Definition 4]{DBLP:journals/siamcomp/DodisORS08} and the accompanying discussion).  Most known constructions of fuzzy extractors are average-case fuzzy extractors.  For simplicity we refer to $\gen', \rep'$ as simply a fuzzy extractor.}  Then $(\gen, \rep)$ is a $(\mathcal{Z}^\gamma, \mathcal{W}, \kappa, t, \gamma\epsilon_{cond}+\epsilon_{fext})$-fuzzy extractor with error $\delta$.

@@

\subsection{More errors than entropy}

In this section we show that \consref{cons:info theoretic} supports partial block sources with more errors than entropy.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  The condenser of Dodis et al~\cite{dodis2014key} has a constant entropy loss, so $\alpha-\tilde{\alpha} = \Theta(1)$. This means that the input entropy to the fuzzy extractor is $\Theta(\gamma)$.   We assume that the new alphabet $\mathcal{Y}$ is of constant size.  Standard fuzzy extractors on constant size alphabets correct a constant fraction of errors at a entropy loss of $\Theta(\gamma)$, yielding $\kappa = \Theta(\gamma)$.  Thus, our construction is secure for distributions with more errors than entropy whenever $|\mathcal{Z}| = \omega(1)$.
More formally:
\[
\text{\# Errors} - \text{Entropy} = \log |B_t| - \Hoo(W) <  t \log |\mathcal{Z}| - \Theta(\gamma)-= \Theta(\gamma) \log |\mathcal{Z}| - \Theta(\gamma)  > 0
\]
That is, there exists a super-constant alphabet size for which \consref{cons:info theoretic} is secure with more errors than entropy.

\section{Adding reusability}
\label{sec:sampling}
In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with more errors than entropy.  Using computational techniques we are able to retain many of the advantages of \consref{cons:info theoretic} and achieve a reusable fuzzy extractor.

The construction samples a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscates the concatenation of these blocks.  Denote this concatenated value by $V_1$.  This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct to ``unlock'' the correct key.  
Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.

@@

\noindent
%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
%\begin{itemize}
%\item Multiple blocks are concatenated together.  This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.  
%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.  This requires the use of digital lockers in place of point obfuscations.  Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.  \consref{cons:first construction} only hid part of the key in each obfuscation.  This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.  This construction works for an arbitrary size alphabet.  We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
%\end{itemize}
The use of a computational primitive~(obfuscation) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.  This is the property that allows reusability.

@@

\subsection{Security of \consref{cons:sampling}}
\label{ssec:sec cons sampling}
%We now return to showing \thref{thm:sampling}.  
In this section we outline security of \consref{cons:sampling}.  A proof of security appears in\apref{sec:analysis sampling}.  
With overwhelming probability, at each of the $\ell$ iterations, the sampler will choose enough coordinates of $W$ that have high entropy, making $V_i$ have sufficient entropy.   Once each of the $V_1,..., V_\ell$ have high entropy the obfuscations are unlikely to return a value other than $\perp$ to an adversary.
% forms a block-unguessable distribution.  Then security essentially follows from the security of \consref{cons:first construction}. %follows very similarly to \lemref{lem:security of cons}~(used to show security of \consref{cons:first construction}).  
%Essentially, the argument is that an adversary will never be able to open a digital locker and thus they learn no information about the key.  %By the same argument of Then \consref{cons:sampling} is just \consref{cons:first construction} applied to $V_1,.., V_\ell$, and security follows by \lemref{lem:security of cons}.  
We begin by showing that each $V_i$ is statistically close to a high entropy distribution.   Let $\Lambda$ represent the random variable of all the coins used by $\sample$ and $\lambda=\lambda_1 \dots \lambda_\ell$
be some particular outcome.

@@

Once all $V_i$ all simultaneously have good entropy, the adversary only sees $\perp$ as an output from the obfuscations~(with overwhelming probability).  If the adversary only sees $\perp$ from the obfuscations, they have no information about the key.

@@

\subsection{Correctness of \consref{cons:sampling}}
\label{sec:correct sampling}
We encode the entire key in each obfuscation.  For correctness, at least one of the repeated readings must be correct with overwhelming probability.  Let $V_i$ represent one of the initial readings and $V_i'$ represent a repeated reading.  For showing correctness we must show that $\Pr[\forall i, V_i \neq V_i'] < \ngl(n)$.

\begin{lemma}[Proof in \apref{sec:analysis sampling}]
\label{lem:sampling errors}
Let all the variables be as in \thref{thm:sampling}.
 Then $\Pr[\forall i, v_i\neq v_i'] < \ngl(n)$, where the probability is over the coins of $\gen$.  
\end{lemma}

\subsection{Reusability of \consref{cons:sampling}}
The reusability of \consref{cons:sampling} follows from the security of the VGB obfuscator with auxiliary input.  We consider a bounded $q = \poly(n)$ number of reuses.  For some fixed $i\in \{1,..., q\}$ we will treat the remaining keys as auxiliary input to the adversary, and the simulator still performs comparably to a distinguisher with access to the obfuscations.  Thus, given sufficiently strong reusability we achieve the following result:
